Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-09-30 WSSSPE3/report/wg_appendix_publishing_SW.tex
Fleshed out appendix.
Former-commit-id: 003d4d20a8350b03d32864245f08748ce674c802

A tentative first cut at the list contains the following:
\begin{itemize}
\item ACM Transactions on Mathematical Software (TOMS) - which provides the extra step
 of having reviewers validate the code which was submitted with the publication.
\item The Mathematica Journal - which publishes Mathematica notebooks (with equations,
figures, etc.) directly.
\item O'Reily Media has announced that it plans to make IPython Notebooks a first-class
 authoring environment for their publishing program alongside their existing mechanisms.
\item Nature is offering a list of notebooks published alongside more traditional articles,
 and is looking at ways to make these documents more official. There are, in fact, a
 number of journals that offer "electronic supplements" to the more traditionally published
 static articles.
\item There is also a list of "reproducible academic publications" maintained here:
  \url{https://github.com/ipython/ipython/wiki/A-gallery-of-interesting-IPython-Notebooks#reproducible-academic-publications}
\end{itemize}

>>>>

A tentative first cut at the list containing executable papers identified the following:

\begin{itemize}
\item ACM Transactions on Mathematical Software (TOMS) - which provides the extra step
 of having reviewers validate the code which was submitted with the publication.
\item The Mathematica Journal - which publishes Mathematica notebooks (with equations,
figures, etc.) directly.
\item O'Reily Media has announced that it plans to make IPython Notebooks a first-class
 authoring environment for their publishing program alongside their existing mechanisms.
\item Nature is offering a list of notebooks published alongside more traditional articles,
 and is looking at ways to make these documents more official. There are, in fact, a
 number of journals that offer "electronic supplements" to the more traditionally published
 static articles.
\item There is also a list of "reproducible academic publications" maintained here:
  \url{https://github.com/ipython/ipython/wiki/A-gallery-of-interesting-IPython-Notebooks#reproducible-academic-publications}
\item KBase narratives build on IPython/Jupyter notebooks to build publications that are
  reproducible, and can be commented or annotated.
\end{itemize}

The group also discussed future possibilities for this new publication format which might
provide advantages.

\begin{itemize}
\item Journals could be built around an existing, widely-used framework thereby reducing
  the burden of studying code on the part of reviewers (common bits of infrastructure
  which aren't relevant to the science would be automatically excluded).
\item Journals might be encouraged to use more metadata, making them easier to mine
  for various analytical purposes.
\item RIO is an effort to publish fragmentary results that can subsequently be combined
  into a single content item.
\item Papers could be made more understandable. Each equation or technical term could
  offer a link to a document/tutorial explaining its origin and/or derivation.
\item So many options for publication currently exist that good science may be getting
  lost in the noise. Would some sort of "upvote" mechanism be of value?
\item Some sort of Replicated Computation Results badge could be made available to
  publications that have undergone greater scrutiny (this is already done by TOMS).
\end{itemize}
